Simple Cache-sensitive Skip list

### 2025-05-07 simple cache-sentive skip list/main.tex
add paper

\documentclass{article}

\newcommand{\keywords}[1]{\par\noindent\textbf{Keywords:} #1}
% Language setting
% Replace `english' with e.g. `spanish' to change the document language
\usepackage[english]{babel}

% Set page size and margins
% Replace `letterpaper' with `a4paper' for UK/EU standard size
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage{tikz}
\usepackage{pgfplots}
\usetikzlibrary{arrows.meta}
% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\SetKw{KwDownTo}{down to}

\title{simple cache-sentive skip list}

\author[1]{Yuchang Ke}
\author[2]{Bill Lv}
\author[3]{Weijie Zhang}

\email[1]{aceking.ke@gmail.com}
\email[2]{ideaalloc@gmail.com}
\email[3]{zhangweijie@gmail.com}

\affil[1]{%
  \institution{} 
  \streetaddress{}
  \city{Wuhan}
  \state{Hubei}
  \postcode{430000}
}
\affil[2]{%
  \institution{} 
  \streetaddress{}
  \city{Wuhan}
  \state{Hubei}
  \postcode{430000}
}
\affil[3]{%
  \institution{Hubei Changjiang Yunxin Media Group Co., Ltd} 
  \streetaddress{No. 788, Gaoxin Ave., Hubei Broadcasting&TV Media Tower}
  \city{Wuhan}
  \state{Hubei}
  \postcode{430000}
}

\begin{document}
\maketitle

\begin{abstract}
      We present a cache-sensitive skiplist that is very simple and easy to implement. It only requires a few small modifications to the original skiplist to adapt it to modern CPU architectures, resulting in a performance improvement of 1.2~1.6 times, in some system it can reach 2X or 3X.
      Unlike other optimizations, it does not require specialized instructions such as SIMD or multi-threaded programming. Instead, it takes advantage of modern compiler optimizations, making it more universal. This design can be used not only in in-memory databases or key-value stores, but also in embedded systems.

\keywords{skiplist; cache-sensitive; index structure}
\end{abstract}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\linewidth]{skiplist.png}
\caption{A simple cache-sensitive skip list}
\label{fig:fig1}
\end{figure}
Our key contributions include: 1. Introducing a vector, which maintains the algorithm's complexity while improving CPU cache hit rate due to its contiguous storage. 2. Reducing the skiplist's level count and pointer overhead by incorporating a vector. 3. Presenting vector-based insertion, search, and deletion algorithms for data nodes, offering a novel perspective for database index design.

@@

\begin{figure}[ht]
      \centering
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,302); %set diagram left start at 0, and has height of 302

%Shape: Rectangle [id:dp802121456728152] 
\draw   (57.79,105.64) -- (118.41,105.64) -- (118.41,130.32) -- (57.79,130.32) -- cycle ;
%Shape: Rectangle [id:dp9825705095547612] 
\draw   (332.28,103.17) -- (392.89,103.17) -- (392.89,127.86) -- (332.28,127.86) -- cycle ;
%Shape: Rectangle [id:dp248949237262718] 
\draw   (246.56,103.79) -- (307.17,103.79) -- (307.17,128.47) -- (246.56,128.47) -- cycle ;
%Shape: Rectangle [id:dp1628354408576529] 
\draw   (153.04,104.41) -- (213.65,104.41) -- (213.65,129.09) -- (153.04,129.09) -- cycle ;
%Shape: Rectangle [id:dp000018829587681290505] 
\draw   (57.79,56.27) -- (118.41,56.27) -- (118.41,80.96) -- (57.79,80.96) -- cycle ;
%Shape: Rectangle [id:dp247562625981687] 
\draw   (57.79,80.96) -- (118.41,80.96) -- (118.41,105.64) -- (57.79,105.64) -- cycle ;
%Shape: Rectangle [id:dp2644216550992282] 
\draw   (540.96,104.41) -- (601.57,104.41) -- (601.57,129.09) -- (540.96,129.09) -- cycle ;
%Shape: Rectangle [id:dp8347359895416517] 
\draw   (540.96,55.04) -- (601.57,55.04) -- (601.57,79.72) -- (540.96,79.72) -- cycle ;
%Shape: Rectangle [id:dp6823901202027933] 
\draw   (540.96,79.72) -- (601.57,79.72) -- (601.57,104.41) -- (540.96,104.41) -- cycle ;
%Shape: Rectangle [id:dp379773497534003] 
\draw   (153.04,79.72) -- (213.65,79.72) -- (213.65,104.41) -- (153.04,104.41) -- cycle ;
%Shape: Rectangle [id:dp8262463980956687] 
\draw   (153.04,55.04) -- (213.65,55.04) -- (213.65,79.72) -- (153.04,79.72) -- cycle ;
%Shape: Rectangle [id:dp618442800182132] 
\draw   (454.37,103.17) -- (514.98,103.17) -- (514.98,127.86) -- (454.37,127.86) -- cycle ;
%Straight Lines [id:da18234761053431092] 
\draw    (118.41,119.22) -- (151.04,119.22) ;
\draw [shift={(153.04,119.22)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da17691354593928432] 
\draw    (213.65,117.98) -- (246.29,117.98) ;
\draw [shift={(248.29,117.98)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da06545360607750506] 
\draw    (306.3,116.13) -- (332.01,116.13) ;
\draw [shift={(334.01,116.13)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da8917793267177494] 
\draw    (392.89,116.75) -- (452.37,117.34) ;
\draw [shift={(454.37,117.36)}, rotate = 180.58] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da6270688079351094] 
\draw    (514.98,116.13) -- (538.96,116.7) ;
\draw [shift={(540.96,116.75)}, rotate = 181.36] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da16483082426708995] 
\draw    (119.27,93.91) -- (151.91,93.91) ;
\draw [shift={(153.91,93.91)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Shape: Rectangle [id:dp8280971824764716] 
\draw   (332.28,78.49) -- (392.89,78.49) -- (392.89,103.17) -- (332.28,103.17) -- cycle ;
%Straight Lines [id:da6251582090553987] 
\draw    (119.27,69.23) -- (151.91,69.23) ;
\draw [shift={(153.91,69.23)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da906622887317923] 
\draw    (214.52,67.38) -- (536.36,67.38) ;
\draw [shift={(538.36,67.38)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da1247883464855224] 
\draw    (214.52,91.45) -- (330.28,92.05) ;
\draw [shift={(332.28,92.06)}, rotate = 180.3] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da5312111106538793] 
\draw    (392.03,91.45) -- (538.96,91.45) ;
\draw [shift={(540.96,91.45)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Curve Lines [id:da7690346774156931] 
\draw    (107.15,66.76) .. controls (141.78,48.25) and (163.43,87.74) .. (198.07,69.23) ;
%Curve Lines [id:da09969258339888487] 
\draw    (198.07,69.23) .. controls (232.7,50.72) and (171.22,109.34) .. (205.86,90.83) ;
%Curve Lines [id:da17301735066569246] 
\draw    (205.86,90.83) .. controls (240.5,72.32) and (331.41,113.66) .. (366.05,95.15) ;
%Curve Lines [id:da04935924618461396] 
\draw    (361.72,97) .. controls (396.36,78.49) and (358.26,135.26) .. (392.89,116.75) ;
%Curve Lines [id:da43861108104506963] 
\draw    (52.6,38.99) .. controls (87.23,20.48) and (72.51,85.27) .. (107.15,66.76) ;
%Shape: Ellipse [id:dp551323556779669] 
\draw   (410.21,92.06) .. controls (410.21,69.57) and (417.19,51.33) .. (425.8,51.33) .. controls (434.4,51.33) and (441.38,69.57) .. (441.38,92.06) .. controls (441.38,114.56) and (434.4,132.79) .. (425.8,132.79) .. controls (417.19,132.79) and (410.21,114.56) .. (410.21,92.06) -- cycle ;
%Straight Lines [id:da9115207752269137] 
\draw    (445.71,32.82) -- (427.26,49.97) ;
\draw [shift={(425.8,51.33)}, rotate = 317.09] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Shape: Rectangle [id:dp44944938443713855] 
\draw   (62.12,221.87) -- (122.73,221.87) -- (122.73,246.55) -- (62.12,246.55) -- cycle ;
%Shape: Rectangle [id:dp8751335667917544] 
\draw   (336.61,219.4) -- (397.22,219.4) -- (397.22,244.08) -- (336.61,244.08) -- cycle ;
%Shape: Rectangle [id:dp2257346710215089] 
\draw   (250.89,220.01) -- (311.5,220.01) -- (311.5,244.7) -- (250.89,244.7) -- cycle ;
%Shape: Rectangle [id:dp8771184949651254] 
\draw   (157.37,220.63) -- (217.98,220.63) -- (217.98,245.32) -- (157.37,245.32) -- cycle ;
%Shape: Rectangle [id:dp5789469841235695] 
\draw   (62.12,172.5) -- (122.73,172.5) -- (122.73,197.18) -- (62.12,197.18) -- cycle ;
%Shape: Rectangle [id:dp5624687649592586] 
\draw   (62.12,197.18) -- (122.73,197.18) -- (122.73,221.87) -- (62.12,221.87) -- cycle ;
%Shape: Rectangle [id:dp13120546674792055] 
\draw   (583.39,220.63) -- (644,220.63) -- (644,245.32) -- (583.39,245.32) -- cycle ;
%Shape: Rectangle [id:dp18910975661576046] 
\draw   (583.39,171.26) -- (644,171.26) -- (644,195.95) -- (583.39,195.95) -- cycle ;
%Shape: Rectangle [id:dp968839873549274] 
\draw   (583.39,195.95) -- (644,195.95) -- (644,220.63) -- (583.39,220.63) -- cycle ;
%Shape: Rectangle [id:dp5100738159249718] 
\draw   (157.37,195.95) -- (217.98,195.95) -- (217.98,220.63) -- (157.37,220.63) -- cycle ;
%Shape: Rectangle [id:dp5130816669129519] 
\draw   (157.37,171.26) -- (217.98,171.26) -- (217.98,195.95) -- (157.37,195.95) -- cycle ;
%Shape: Rectangle [id:dp10069788621732956] 
\draw   (495.07,219.4) -- (555.68,219.4) -- (555.68,244.08) -- (495.07,244.08) -- cycle ;
%Straight Lines [id:da7506949131852723] 
\draw    (122.73,235.44) -- (155.37,235.44) ;
\draw [shift={(157.37,235.44)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da5055411274108006] 
\draw    (217.98,234.21) -- (250.62,234.21) ;
\draw [shift={(252.62,234.21)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da7559298876477776] 
\draw    (310.63,232.36) -- (336.34,232.36) ;
\draw [shift={(338.34,232.36)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da08581070094109111] 
\draw    (397.22,232.97) -- (414.27,233.62) ;
\draw [shift={(416.27,233.7)}, rotate = 182.18] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da5858905620692174] 
\draw    (557.41,232.36) -- (581.39,232.93) ;
\draw [shift={(583.39,232.97)}, rotate = 181.36] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da32674036346427937] 
\draw    (123.6,210.14) -- (156.24,210.14) ;
\draw [shift={(158.24,210.14)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Shape: Rectangle [id:dp026479095509071682] 
\draw   (336.61,194.71) -- (397.22,194.71) -- (397.22,219.4) -- (336.61,219.4) -- cycle ;
%Straight Lines [id:da5236391813651351] 
\draw    (123.6,185.46) -- (156.24,185.46) ;
\draw [shift={(158.24,185.46)}, rotate = 180] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da951241427709963] 
\draw    (219.71,183.96) -- (578.79,183.61) ;
\draw [shift={(580.79,183.61)}, rotate = 179.94] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da5677734486818795] 
\draw    (218.85,207.67) -- (334.61,208.28) ;
\draw [shift={(336.61,208.29)}, rotate = 180.3] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Straight Lines [id:da03778045413284792] 
\draw    (397.22,207.61) -- (581.39,207.67) ;
\draw [shift={(583.39,207.67)}, rotate = 180.02] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;
%Shape: Rectangle [id:dp9874088035206192] 
\draw   (416.27,219.4) -- (476.88,219.4) -- (476.88,244.08) -- (416.27,244.08) -- cycle ;
%Straight Lines [id:da719219755060643] 
\draw    (476.02,232.97) -- (493.07,233.62) ;
\draw [shift={(495.07,233.7)}, rotate = 182.18] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

% Text Node
\draw (170.55,108.56) node [anchor=north west][inner sep=0.75pt]   [align=left] {3,4};
% Text Node
\draw (264.06,109.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {5,6};
% Text Node
\draw (349.79,107.94) node [anchor=north west][inner sep=0.75pt]   [align=left] {7,9};
% Text Node
\draw (470.74,107.94) node [anchor=north west][inner sep=0.75pt]   [align=left] {12,17};
% Text Node
\draw (174.82,85.72) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
% Text Node
\draw (177.41,60.42) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
% Text Node
\draw (352.32,82.64) node [anchor=north west][inner sep=0.75pt]   [align=left] {7};
% Text Node
\draw (76.23,40.06) node [anchor=north west][inner sep=0.75pt]   [align=left] {head};
% Text Node
\draw (553.41,39.44) node [anchor=north west][inner sep=0.75pt]   [align=left] {tail};
% Text Node
\draw (564.06,59.8) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
% Text Node
\draw (564.06,85.72) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
% Text Node
\draw (562.33,106.7) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
% Text Node
\draw (45.5,20.51) node [anchor=north west][inner sep=0.75pt]   [align=left] {search path};
% Text Node
\draw (435.12,22.78) node [anchor=north west][inner sep=0.75pt]   [align=left] {update[i] →forward[i] };
% Text Node
\draw (265.32,141.26) node [anchor=north west][inner sep=0.75pt]   [align=left] {original list, 8 to be inserted};
% Text Node
\draw (174.88,224.78) node [anchor=north west][inner sep=0.75pt]   [align=left] {3,4};
% Text Node
\draw (268.39,225.4) node [anchor=north west][inner sep=0.75pt]   [align=left] {5,6};
% Text Node
\draw (354.12,224.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {7,8};
% Text Node
\draw (505.37,224.17) node [anchor=north west][inner sep=0.75pt]   [align=left] {12,17};
% Text Node
\draw (179.15,201.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
% Text Node
\draw (181.74,176.65) node [anchor=north west][inner sep=0.75pt]   [align=left] {3};
% Text Node
\draw (356.65,198.86) node [anchor=north west][inner sep=0.75pt]   [align=left] {7};
% Text Node
\draw (80.56,156.28) node [anchor=north west][inner sep=0.75pt]   [align=left] {head};
% Text Node
\draw (595.83,155.67) node [anchor=north west][inner sep=0.75pt]   [align=left] {tail};
% Text Node
\draw (606.49,176.03) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
% Text Node
\draw (606.49,201.95) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
% Text Node
\draw (604.76,222.93) node [anchor=north west][inner sep=0.75pt]   [align=left] {nil};
% Text Node
\draw (431.99,223.16) node [anchor=north west][inner sep=0.75pt]   [align=left] {9};
% Text Node
\draw (267.41,246.44) node [anchor=north west][inner sep=0.75pt]   [align=left] {list after insertation};

\end{tikzpicture}
\caption{insert 8 into simple cache-sentive skip list(max array size =2)}
\label{fig:fig2}
\end{figure}

@@

\subsection{Search}
\begin{algorithm}[H]
    \caption{Search Key in simple cache-sentive skip list}
    \KwIn{Key $k$}
    \KwOut{Node containing key or Nil}
    \SetKwFunction{FMain}{search}
    \SetKwProg{Fn}{Function}{:}{}
    \Fn{\FMain{$k$}}{
        $current \gets header$\;

@@

\subsection{Insertion}
\begin{algorithm}[H]
    \caption{Insert Key into simple cache-sentive skip list}
    \KwIn{Key $k$}
    \KwOut{Nil}
    \SetKwFunction{FMain}{insert}
    \SetKwProg{Fn}{Function}{:}{}
    \Fn{\FMain{$k$}}{
        $update \gets \text{array of size } (max\_level + 1)$\;
        $current \gets header$\;

@@

\begin{algorithm}[H]
        \caption{Delete key from simple cache-sentive skip list}
        \KwIn{Key $k$}
        \KwOut{True if deleted, False otherwise}
        \SetKwFunction{FMain}{delete}
        \SetKwProg{Fn}{Function}{:}{}
        \Fn{\FMain{$k$}}{
            $update \gets \text{array of size } (max\_level + 1)$\;
            $current \gets header$\;

@@

\subsection{Performace}
\begin{figure}[htbp]
\centering
\begin{tikzpicture}
\begin{axis}[
    ybar,
    bar width=10pt,
    width=14cm,
    height=9cm,
    enlarge x limits=0.1,
    xlabel={Size},
    ylabel={Time (µs)},
    symbolic x coords={100,1000,5000,10000,20000,50000,200000,250000,300000},
    xtick=data,
    legend style={at={(0.5,-0.15)},anchor=north,legend columns=2},
    nodes near coords,
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west},
    ymin=0,
    ymajorgrids=true,
    grid style=dashed
]
\addplot+[style={blue,fill=blue!30}] coordinates {
    (100,19) (1000,222) (5000,1383) (10000,2654)  (20000,4474) (50000,11040) (200000,51209) (250000,66618) (300000,81313)
};
\addplot+[style={red,fill=red!30}] coordinates {
    (100,14) (1000,174) (5000,994) (10000,2070)  (20000,2936) (50000,6986) (200000,30934) (250000,41203) (300000,51843)
};

@@

\begin{figure}[htbp]
\begin{tikzpicture}
\begin{axis}[
    width=14cm,
    height=8cm,
    ybar,
    bar width=12pt,
    symbolic x coords={100,1000,5000,10000,20000,50000,200000,250000,300000},
    xtick=data,
    xlabel={Data Size},
    ylabel={Time (µs)},
    legend style={at={(0.5,-0.2)},anchor=north,legend columns=-1},
    enlarge x limits=0.08,
    ymin=0,
    grid=major,
    nodes near coords,
    nodes near coords style={font=\small, anchor=west, rotate=90, xshift=4pt},
]

@@

We evaluated the standard skip list and SCSL with a maximum level of 16. Figure 3 presents the insertion performance comparison between the standard skip list and simple cache skip list in a Macbook. It shows that under small scale of data (< 1000) simple cache skip list can speed up to 1.28~1.39 times, and under medium scale (over 20000) , it can speed up to 1.55~1.65 times, as the scale increasing, the more benefit for performance. Figure 4 also shows that, in server computer, the simple cache skip list can speed up even 3 times.
\begin{table}
\begin{tabular}{lrrr}
\toprule
Test Case & Cache References & Cache Misses & Cache Miss Rate \\
\midrule
SCSL & 51,567,218 & 459,636 & 0.89\% \\
Standard Skip List & 142,249,678 & 47,251,323 & 33.22\% \\
\bottomrule
\end{tabular}
\caption{Cache Performance Comparison Between SCSL and standard Skip list in server computer}
\end{table}

As shown in the table above(table 1), the standard skip list in the test achieves a 33.22\% cache-miss rate, whereas SCSL has only a 0.89\% cache-miss rate. It also proves that adding arrays to data nodes can work very well.

>>>>

% VLDB template version of 2020-08-03 enhances the ACM template, version 1.7.0:
% https://www.acm.org/publications/proceedings-template
% The ACM Latex guide provides further information about the ACM template

\documentclass[sigconf, nonacm, letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{acmart}

%% The following content must be adapted for the final version
% paper-specific
\newcommand\vldbdoi{XX.XX/XXX.XX}
\newcommand\vldbpages{XXX-XXX}
% issue-specific
\newcommand\vldbvolume{19}
\newcommand\vldbissue{1}
\newcommand\vldbyear{2025}
% should be fine as it is
\newcommand\vldbauthors{\authors}
\newcommand\vldbtitle{\shorttitle} 
% leave empty if no availability url should be set
\newcommand\vldbavailabilityurl{}
% whether page numbers should be shown or not, use 'plain' for review versions, 'empty' for camera ready
\newcommand\vldbpagestyle{plain}

\usepackage{adjustbox}
\usepackage{pgfplots}
\usetikzlibrary{arrows.meta}
% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\SetKw{KwDownTo}{down to}
\begin{document}
\title{Simple Cache-sensitive Skip list}

%%
%% The "author" command and its associated commands are used to define the authors and their affiliations.
\author{Yuchang Ke}
\affiliation{%
  \institution{independent researcher}
  \streetaddress{No. 12, Guandong Street, Hongshan District, Wuhan, Hubei Province.}
  \city{Wuhan}
  \state{China}
  \postcode{430073}
}
\email{aceking.ke@gmail.com}

\author{Bill Lv}
\email{ideaalloc@gmail.com}

\author{Weijie Zhang}
\email{zhangweijie@gmail.com}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
      We present a cache-sensitive skiplist that is very simple and easy to implement. It only requires a few small modifications to the original skiplist to adapt it to modern CPU architectures, resulting in a performance improvement of 1.2~1.6 times, in some system it can reach 2X or 3X.
      Unlike other optimizations, it does not require specialized instructions such as SIMD or multi-threaded programming. Instead, it takes advantage of modern compiler optimizations, making it more universal. This design can be used not only in in-memory databases or key-value stores, but also in embedded systems.  here is \href{https://github.com/acekingke/simpleCacheSentiveSkiplist}{github link}
\keywords{skiplist; cache-sensitive; index structure}

\end{abstract}

\maketitle

%%% do not modify the following VLDB block %%
%%% VLDB block start %%%
\pagestyle{\vldbpagestyle}
\begingroup\small\noindent\raggedright\textbf{PVLDB Reference Format:}\\
\vldbauthors. \vldbtitle. PVLDB, \vldbvolume(\vldbissue): \vldbpages, \vldbyear.\\
\href{https://doi.org/\vldbdoi}{doi:\vldbdoi}
\endgroup
\begingroup
\renewcommand\thefootnote{}\footnote{\noindent
This work is licensed under the Creative Commons BY-NC-ND 4.0 International License. Visit \url{https://creativecommons.org/licenses/by-nc-nd/4.0/} to view a copy of this license. For any use beyond those covered by this license, obtain permission by emailing \href{mailto:info@vldb.org}{info@vldb.org}. Copyright is held by the owner/author(s). Publication rights licensed to the VLDB Endowment. \\
\raggedright Proceedings of the VLDB Endowment, Vol. \vldbvolume, No. \vldbissue\ %
ISSN 2150-8097. \\
\href{https://doi.org/\vldbdoi}{doi:\vldbdoi} \\
}\addtocounter{footnote}{-1}\endgroup
%%% VLDB block end %%%

%%% do not modify the following VLDB block %%
%%% VLDB block start %%%
\ifdefempty{\vldbavailabilityurl}{}{
\vspace{.3cm}
\begingroup\small\noindent\raggedright\textbf{PVLDB Artifact Availability:}\\
The source code, data, and/or other artifacts have been made available at \url{\vldbavailabilityurl}.
\endgroup
}
%%% VLDB block end %%%

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figures/skiplist.png}
\caption{A simple cache-sensitive skip list}
  \label{fig:skiplist}
\end{figure}

Our key contributions include: 1. Introducing a vector, which maintains the algorithm's complexity while improving CPU cache hit rate due to its contiguous storage. 2. Reducing the skiplist's level count and pointer overhead by incorporating a vector. 3. Presenting vector-based insertion, search, and deletion algorithms for data nodes, offering a novel perspective for database index design.

@@

\begin{figure}
      \centering
  \includegraphics[width=\linewidth]{figures/skipinsert.jpg}
\caption{insert 8 into simple cache-sentive skip list(max array size =2)}
\label{fig:fig2}
\end{figure}

@@

\subsection{Search}
\begin{algorithm}
    \caption{Search Key in simple cache-sentive skip list}
    \KwIn{Key $k$}
    \KwOut{Node containing key or Nil}
    \SetKwFunction{FMain}{search}
    \SetKwProg{Fn}{Function}{:}{}
    \Fn{\FMain{$k$}}{
        $current \gets header$\;

@@

\subsection{Insertion}
\begin{algorithm}
    \caption{Insert Key into simple cache-sentive skip list}
    \KwIn{Key $k$}
    \KwOut{Nil}
    \SetKwFunction{FMain}{insert}
    \SetKwProg{Fn}{Function}{:}{}
    \Fn{\FMain{$k$}}{
        $update \gets \text{array of size } (max\_level + 1)$\;
        $current \gets header$\;

@@

\begin{algorithm}
        \caption{Delete key from simple cache-sentive skip list}
        \KwIn{Key $k$}
        \KwOut{True if deleted, False otherwise}
        \SetKwFunction{FMain}{delete}
        \SetKwProg{Fn}{Function}{:}{}
        \Fn{\FMain{$k$}}{
            $update \gets \text{array of size } (max\_level + 1)$\;
            $current \gets header$\;

@@

\subsection{Performace}
\begin{figure}
\centering
\begin{tikzpicture}[scale=0.6]
\begin{axis}[
    ybar,
    bar width=10pt,
    width=14cm,
    height=9cm,
    enlarge x limits=0.1,
    xlabel={Size},
    ylabel={Time (µs)},
    symbolic x coords={100,1000,5000,10000,20000,50000,200000,250000,300000},
    xtick=data,
    legend style={at={(0.5,-0.15)},anchor=north,legend columns=2},
    nodes near coords,
    every node near coord/.append style={font=\tiny, rotate=90, anchor=west},
    ymin=0,
    ymajorgrids=true,
    grid style=dashed
]
\addplot+[style={blue,fill=blue!30}] coordinates {
    (100,19) (1000,222) (5000,1383) (10000,2654)  (20000,4474) (50000,11040) (200000,51209) (250000,66618) (300000,81313)
};
\addplot+[style={red,fill=red!30}] coordinates {
    (100,14) (1000,174) (5000,994) (10000,2070)  (20000,2936) (50000,6986) (200000,30934) (250000,41203) (300000,51843)
};

@@

\begin{figure}
\begin{tikzpicture}[scale=0.6]
\begin{axis}[
    width=14cm,
    height=8cm,
    ybar,
    bar width=12pt,
    symbolic x coords={100,1000,5000,10000,20000,50000,200000,250000,300000},
    xtick=data,
    xlabel={Data Size},
    ylabel={Time (µs)},
    legend style={at={(0.5,-0.2)},anchor=north,legend columns=-1},
    enlarge x limits=0.08,
    ymin=0,
    grid=major,
    nodes near coords,
    nodes near coords style={font=\small, anchor=west, rotate=90, xshift=4pt},
]

@@

We evaluated the standard skip list and SCSL with a maximum level of 16. Figure 3 presents the insertion performance comparison between the standard skip list and simple cache skip list in a Macbook. It shows that under small scale of data (< 1000) simple cache skip list can speed up to 1.28~1.39 times, and under medium scale (over 20000) , it can speed up to 1.55~1.65 times, as the scale increasing, the more benefit for performance. Figure 4 also shows that, in server computer, the simple cache skip list can speed up even 3 times.
\begin{table*}[t]
\begin{tabular}{lrrr}
\toprule
Test Case & Cache References & Cache Misses & Cache Misses Rate \\
\midrule
\verb|SCSL| & 51,567,218 & 459,636 & 0.89\% \\
\verb|Standard Skip List| & 142,249,678 & 47,251,323 & 33.22\% \\
\bottomrule
\end{tabular}
\caption{Cache Performance Comparison Between SCSL and standard Skip list in server computer}
\end{table*}
As shown in the table above(table 1), the standard skip list in the test achieves a 33.22\% cache-miss rate, whereas SCSL has only a 0.89\% cache-miss rate. It also proves that adding arrays to data nodes can work very well.
